Biden Expected to Win 54% of Popular Vote in 2020 US Presidential Election

### 2020-11-02 outputs/paper/paper.Rmd
the most insane
Update?

---
title: "Biden Expected to Win 54% of Popular Vote in 2020 US Presidential Election"
subtitle: "4% Confidence Interval Based on a Survey from June 2020"
author: "James Bao, Zakir Chaudry, Alan Chen, Xinyi Zhang"
date: "`r format(Sys.time(), '%d %B %Y')`"
thanks: "Code and data supporting this analysis are available at: https://github.com/JamesBond0014/sta304_ps4."
abstract: |
  | First sentence, second sentence, third sentence, fourth sentence
  |
  | **Keywords:** forecasting, US 2020 Election, Trump, Biden, multilevel regression with post-stratification

@@

# Abstract
After a shocking upset in the 2016 US Presidential election, everyone has their eyes on the 2020 election to determine the leader of the free world for the next four years. In this Paper we trained a model using survey level survey results . Our model predicts that Joe Biden will win the 2020 Presidential election with a 53.5% of the popular vote and a confidence level of 95%. Our prediction as well as our breakdown of votes by demographic group could potentially provide the candidates of the election with information on how to target voters.

@@

```{r eval=FALSE}
cleaned_data <- labelled::to_factor(cleaned_data)

# Plot Race
perc_race <- cleaned_data %>% count(race_ethnicity) %>% mutate(perc = n/nrow(cleaned_data))
race <- perc_race %>% ggplot(aes(x = race_ethnicity, y = perc)) + geom_bar(stat = "identity") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) + labs(title = "Race/Ethnicity of Respondents in 2018 ACS data",
                                                                               x = "Race/Ethnicity", y = "Percentage", subtitle = "Figure X")
race

>>>>

---
title: "Biden Expected to Win 54% of Popular Vote in 2020 US Presidential Election"
subtitle: "4% Confidence Interval Based on a Survey from June 2020"
author: "James Bao, Zakir Chaudry, Alan Chen, Xinyi Zhang"
date: "`r format(Sys.time(), '%d %B %Y')`"
thanks: "Code and data supporting this analysis are available at: https://github.com/JamesBond0014/sta304_ps4."
abstract: |
  | After a shocking upset in the 2016 US Presidential election, everyone has their eyes on the 2020 election to determine the leader of the free world for the next four years. In this Paper we trained a model using survey level survey results . Our model predicts that Joe Biden will win the 2020 Presidential election with a 53.5% of the popular vote and a confidence level of 95%. Our prediction as well as our breakdown of votes by demographic group could potentially provide the candidates of the election with information on how to target voters.
  |
  | **Keywords:** forecasting, US 2020 Election, Trump, Biden, multilevel regression with post-stratification

@@

@@

```{r}
# Plot Race
perc_race <- cleaned_data %>% count(race_ethnicity) %>% mutate(perc = n/nrow(cleaned_data))
race <- perc_race %>% ggplot(aes(x = race_ethnicity, y = perc)) + geom_bar(stat = "identity") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) + labs(title = "Race/Ethnicity of Respondents in 2018 ACS data",
                                                                               x = "Race/Ethnicity", y = "Percentage", subtitle = "Figure X")
race
